%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Huu An Duc (Jack) Le \\ \vspace{1pt}}
    \small +1 416-617-3686 $|$ \href{mailto:x@x.com}{\underline{huuanducle\@gmail.com}} $|$
    \href{https://linkedin.com/in/...}{\underline{www.linkedin.com/in/huu-an-duc-le}} $|$
    \href{https://github.com/...}{\underline{...}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
    {University of Toronto}{}
    {Majoring in Computer Science and Applied Mathematics - GPA: 3.86}{Canada}
    \resumeSubheading
    {British International School, Ho Chi Minh city}{}
    {International Baccalaureate Diploma - GPA: 3.85}{Vietnam}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tutoring and Mentorship}{September, 2022 - Present}
      {University of Toronto \& British International School, Canada}{}
      \resumeItemListStart
        \resumeItem{Collaborated with peers to facilitate weekly tutoring sessions for first-year University of Toronto students in Mathematics and Computer Science.}
        \resumeItem{Revolutionized study materials and presentations through innovative customization, integrating self-edited videos to actively engage learners and streamline intricate concepts.}
        \resumeItem{Guided and led a group of over 30 secondary students, leading to an average 20\% increase in grades.}
        
      \resumeItemListEnd
    \resumeSubheading
      {Productivity Application for British International School Students}{January, 2021 - Present}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Collaborated with the Computer Science department at BIS to enhance and develop "The Planner" application for students.}
        \resumeItem{Collaborated with the researcher group and department heads of Computer Science and Wellbeing faculty to develop a user-friendly platform, integrating computer science fundamentals and object-oriented design to ensure reliability for students and parents.}
        \resumeItem{Drive the attainment of over 300 downloads collectively on primary and secondary campuses while extending the distribution reach.}
        
      \resumeItemListEnd
    \resumeSubheading
      {Design Technology Ambassador}{May, 2020 - July, 2024}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Conducted departmental orientation sessions to familiarize families and students with Design Technology using engaging presentations and interactive 3D software to effectively involve participants.}
        \resumeItem{Included hands-on die-casting and aluminum crafting activities.}
        
      \resumeItemListEnd
    \resumeSubheading
      {Content Creation \& Video Editing}{November, 2022 - May, 2024}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Managed a YouTube channel with 14,000 members, 2.5 million viewers, with 4 years of video editing experience.}
        \resumeItem{Freelance work on 12 projects for 5 international clients.}
        
      \resumeItemListEnd
    
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd



%-----------VOLUNTEER-----------

\section{Volunteer Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {President, Design Now Club}{September, 2023 - May, 2024}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Facilitated hands-on woodworking activities, guided students in utilizing CAD software for 3D printing, and created a dynamic learning environment.}
        
      \resumeItemListEnd
    \resumeSubheading
      {British International School Prefect Team}{December, 2022 - May, 2024}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Led school orientation events to welcome new parents and students, fostering an inclusive and welcoming environment.}
        \resumeItem{Managed and oversaw the "Introduction to Computer Science" workshop, featuring Micro:bit robotics and block-based programming demonstrations for parents to highlight computer science fundamentals and programming languages.}
        
      \resumeItemListEnd
    \resumeSubheading
      {Vice-president, Create and Care Club}{September, 2022 - January, 2024}
      {Vietnam}{}
      \resumeItemListStart
        \resumeItem{Led a team in instructing local students on creating handmade products, such as clay models and accessories.}
        \resumeItem{Successfully engaged with attendees and drove revenue by managing sales activities during seasonal events.}
        
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Proficient: }Python, C\#, HTML, CSS, Javascript, SQL \\
     \textbf{Intermediate: }Java, C++, Perl \\
     \textbf{Technologies: }Adobe Premiere Pro, Adobe Photoshop, Microsoft Office \\
     \textbf{Soft skills: }Creativity, Curious, Big thinker, Adaptable, Collaborative, Adaptability, Innovative, Self-management, Problem-solving, Visionary, Quick learning, Customer obsession, Effective communication, Agile, Personal growth, Empowered \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}